Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2024-03-22 2_SSL_NE/article/article_main.tex
added draft of domain definition

In Supplementary Note 6, we also provide a comparison of the outcomes of our model with past cost calculations and projections published by the U.S. Department of Energy (DOE) on the basis of the \textit{LEDCOM} cost model \cite{ledcomv2} and industry data reported to the DOE as part of SSL round tables.

>>>>

In Supplementary Note 6, we also provide a comparison of our model results with past cost report and projections published by the U.S. Department of Energy (DOE) on the basis of the \textit{LEDCOM} cost model \cite{ledcomv2} and industry data reported as part of SSL round table meetings.

### 2024-03-22 2_SSL_NE/article/article_supplementary.tex
added draft of domain definition

% layout
\input{2_SSL_NE/article/auxiliary/preamble/2_preamble_layout_paperdraft}

@@

>>>>

% layout
\input{auxiliary/preamble/2_preamble_layout_paperdraft}

% formatting
\input{auxiliary/preamble/3_preamble_formatting_listings}

@@

\clearpage
\section{Domain Definition}
\label{sec:domain}

\textit{Elsevier Scopus}\footnote{\url{https://www.scopus.com/search/}} advanced search query:

\begin{pseudocode}
TITLE-ABS-KEY(("light-emitting" OR "light emitting") AND "diode")
AND NOT
TITLE-ABS-KEY(solar OR violet OR laser)
AND NOT
TITLE-ABS-KEY(perovskite OR GaAsP OR AlGaInP OR GaAlAs OR ZnO)
AND NOT
TITLE-ABS-KEY(organic OR polymer*)
AND NOT
SUBJAREA(ARTS OR BUSI OR DECI OR ECON OR PSYC OR SOCI)
AND NOT
SUBJAREA(MEDI OR NURS OR VETE OR DENT OR HEAL OR MULT)
AND NOT
SUBJAREA(AGRI OR BIOC OR IMMU OR NEUR OR PHAR)
AND NOT
SUBJAREA(envi OR EART OR comp)
\end{pseudocode}

Something about patents also?
